Estimating learning dynamics in the routing game

### 2015-10-11 paper/paper.tex
Progress commit

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/no_slider_players_costs.png}
  \caption{Player normalized cost for no slider version.}
  \label{fig:cost_no_slider}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/no_slider_KL_divergence_surface.png}
  \caption{KL Divergence surface.}
  \label{fig:kl_divergence_surface}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/no_slider_players_costs}
  \caption{Player normalized cost for no slider version.}
  \label{fig:cost_no_slider}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/no_slider_KL_divergence_surface}
  \caption{KL Divergence surface.}
  \label{fig:kl_divergence_surface}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/no_slider_global_potential_function}
  \caption{Global potential function.}
  \label{fig:global_potential_function}
\end{figure}
